Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-08-03 documents/ms.tex
adding the table stubb back in

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth, clip=true]{figures/koi_lc_demo.pdf}
\caption[A light curve with a GP model.]
{Light curve of KIC \kepexample, an active star with a rotation period of
$\sim$ \kepexampleperiod\ days.
The blue line shows a fit to the data using a Gaussian process model with a QP
covariance kernel function.}
\label{fig:GP_example}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{figures/corner_plot.pdf}
\caption{Marginal posterior PDFs of the QP GP model parameters, fit to the
    simulated light curve in figure \ref{fig:demo_lc}.
    The blue line in the period panel shows the injected period.
    This figure was made using \texttt{corner.py} \citep{Corner}.}
\label{fig:gp_posteriors}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth, clip=true]{figures/demo_ACF.pdf}
\caption[ACF of a simulated light curve.]
{An autocorrelation function of the simulated light curve shown in figure
\ref{fig:demo_lc}.
The vertical blue line shows the period measured using the ACF method (20.4
days) and the pink dashed line shows the period that was used to simulate the
light curve (\aigrainexampleperiod\ days).}
\label{fig:demo_acf}
\end{center}
\end{figure}

@@

Figure \ref{fig:mcquillan} compares the periods inferred with the GP method to
the ACF-based periods from \citet{Mcquillan2013} for the \nkoimcq\ overlapping
KOIs.
This comparison shows generally very good agreement, demonstrating that this
method works not only on simulated data, but also on real data---with the
caveat that for any particular data set, some care is needed regarding the
setting the priors and ranges for the GP hyperparameters.
% Notably, the GP method recovers periods systematically slightly larger than
% \citet{Mcquillan2013}---a likely consequence of correcting for the ACF peak
% measurement bias discussed in Section \ref{sec:acf}.
\response{The new GP rotation periods calculated for \nkoi\ KOIs are provided in an
online table accompanying this paper.
% The first few lines of this table is shown below
% (table \ref{tab:koi_periods}).
Samples of the rotation period posterior PDFs are available online:
\url{https://doi.org/10.5281/zenodo.804440}}

% \begin{table*}
% \begin{center}
%     \caption{Rotation periods and \Kepler\ input catalogue (KIC) properties
%     for the \Kepler\ objects of interest. The full table is available online.}
% \begin{tabular}{lcccc}
%     KOI number & Period (days) & KIC T$_{\mathrm{eff}}$ & KIC $\log(g)$ & KIC
%     $[$Fe$/$H$]$ \\
%     \hline
%     1 & 25$\pm1$ & $5126^{+160}_{-138}$ & $4.61^{+0.03}_{-0.1}$ &
%     $-0.1\pm0.3$ \\
%     2 & 20$\pm1$ & $5850\pm50$ & $4.46\pm0.03$ & $-0.2\pm0.1$ \\
%     3 & 28$\pm1$ & $6350\pm80$ & $4.02\pm0.01$ & $0.26\pm0.08$\\
%     6 & 23$\pm1$ & $6225^{+114}_{-158}$ & $4.17^{+0.06}_{-0.05}$ &
%     $-0.0^{+0.1}_{-0.2}$\\
%     7 & 25$\pm1$ & $5543\pm79 $ & $4.08\pm0.01$ & $0.4\pm0.1$ \\
%     ... & ... & ... & ... & ... \\
% \end{tabular}
% \end{center}
% \end{table*}
% \label{tab:koi_periods}

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{figures/comparison_koi_01_23.pdf}
\caption[Comparison with McQuillan results.]
{A comparison of our GP rotation period measurements to those of
\citet{Mcquillan2013}.
The data points are coloured by the range of variability measured by
    \citet{Mcquillan2013}, defined as the interval between the 5th and 95th
    percentiles of normalised flux per period bin in millimagnitudes.}
\label{fig:mcquillan}
\end{center}
\end{figure*}

@@

\bibliographystyle{plainnat}
\bibliography{GProtation}
\end{document}

>>>>

% Figure list:
% koi_lc_demo.pdf
% period_hist.pdf
% demo_lc.pdf
% comparison_acfprior_03_10.pdf
% comparison_noprior_02_13.pdf
% corner_plot.pdf
% demo_ACF.pdf
% compare_acf.pdf
% compare_pgram_filtered_35.pdf
% comparison_koi_01_23.pdf

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth, clip=true]{figures/koi_lc_demo.pdf}
\caption[A light curve with a GP model.]
{Light curve of KIC \kepexample, an active star with a rotation period of
$\sim$ \kepexampleperiod\ days.
The solid line shows a fit to the data using a Gaussian process model with a QP
covariance kernel function.}
\label{fig:GP_example}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{figures/corner_plot.pdf}
\caption{Marginal posterior PDFs of the QP GP model parameters, fit to the
    simulated light curve in figure \ref{fig:demo_lc}.
    The solid line in the period panel shows the injected period.
    This figure was made using \texttt{corner.py} \citep{Corner}.}
\label{fig:gp_posteriors}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth, clip=true]{figures/demo_ACF.pdf}
\caption[ACF of a simulated light curve.]
{An autocorrelation function of the simulated light curve shown in figure
\ref{fig:demo_lc}.
The vertical solid blue line shows the period measured using the ACF method (20.4
days) and the pink dashed line shows the period that was used to simulate the
light curve (\aigrainexampleperiod\ days).}
\label{fig:demo_acf}
\end{center}
\end{figure}

@@

Figure \ref{fig:mcquillan} compares the periods inferred with the GP method to
the ACF-based periods from \citet{Mcquillan2013} for the \nkoimcq\ overlapping
KOIs.
This comparison shows generally very good agreement, demonstrating that this
method works not only on simulated data, but also on real data---with the
caveat that for any particular data set, some care is needed regarding the
setting the priors and ranges for the GP hyperparameters.
% Notably, the GP method recovers periods systematically slightly larger than
% \citet{Mcquillan2013}---a likely consequence of correcting for the ACF peak
% measurement bias discussed in Section \ref{sec:acf}.
\response{The new GP rotation periods calculated for \nkoi\ KOIs are provided in an
online table accompanying this paper.
The first few lines of this table is shown below
(table \ref{tab:koi_periods}).
Samples of the rotation period posterior PDFs are available online:
\url{https://doi.org/10.5281/zenodo.804440}}

\begin{table*}
\begin{center}
    \caption{Rotation periods and \Kepler\ input catalogue (KIC) properties
    for the \Kepler\ objects of interest. The full table is available online.}
\begin{tabular}{lcccc}
    KOI number & Period (days) & KIC T$_{\mathrm{eff}} (K)$ & KIC $\log(g)$ &
    KIC $[$Fe$/$H$]$ \\
    \hline
1 & 25$^{+23}_{-6}$ & $5126^{+160}_{-138}$ & $4.61^{+0.03}_{-0.11}$ & $-0.12\pm0.3$\\
2 & 20$\pm4$ & $5850\pm50$ & $4.46\pm0.03$ & $-0.15\pm0.1$\\
3 & 28$^{+3}_{-0.2}$ & $6350\pm80$ & $4.02\pm0.01$ & $0.26\pm0.08$\\
6 & 23$^{+3}_{-15}$ & $6225^{+114}_{-158}$ & $4.17^{+0.06}_{-0.05}$ & $-0.04^{+0.1}_{-0.2}$\\
7 & 25$\pm2$ & $5543\pm79$ & $4.08\pm0.01$ & $0.44\pm0.1$\\
    ... & ... & ... & ... & ... \\
\end{tabular}
\end{center}
\end{table*}
\label{tab:koi_periods}

\begin{figure*}
\begin{center}
\includegraphics[width=6in, clip=true]{figures/comparison_koi_01_23.pdf}
\caption[Comparison with McQuillan results.]
{A comparison of our GP rotation period measurements to those of
\citet{Mcquillan2013}.
The data points are coloured by the range of variability measured by
    \citet{Mcquillan2013}, defined as the interval between the 5th and 95th
    percentiles of normalized flux per period bin in millimagnitudes.}
\label{fig:mcquillan}
\end{center}
\end{figure*}

@@

% \bibliographystyle{plainnat}
\bibliographystyle{hapj}
\bibliography{GProtation}
\end{document}
